---
title: "UWLC report"
output: 
  html_notebook:
    toc: yes
    toc_float: true
---

#Clear environment
```{r}
rm(list=ls())
```

#Load Libraries
```{r, message = FALSE}
library(tidyverse)
library(haven)
library(readxl)
```

#Read in data
```{r, message = FALSE}

s18_pre_post <- read_sas("T:/Research folders/CCWTG/Data/Spring2018/FINALDATA/mentees.sas7bdat")
master       <- read_sas("T:/Research folders/CCWTG/Data/Spring2018/FINALDATA/MASTER.sas7bdat")

f18_drop     <- read_excel("R:/For CC Program/Fall 2018/Youth Recruitment/FALL18 Intake Master Tracking.xlsx", sheet = "Dropped")
f18_intake   <- read_excel("R:/For CC Program/Fall 2018/Youth Recruitment/FALL18 Intake Master Tracking.xlsx", sheet = 1)

headers <- names(read_csv("../Data/F18/F18_Youth_Intake.csv", n_max = 0))
f18_pre <- read_csv("../Data/F18/F18_Youth_Intake.csv", skip = 3, col_names = FALSE)
colnames(f18_pre) <- headers
rm(headers)

headers <-  names(read_csv("../Data/F18/F18_Youth_Post.csv", n_max = 0))
f18_post <- read_csv("../Data/F18/F18_Youth_Post.csv", skip = 3, col_names = FALSE)
colnames(f18_post) <- headers
rm(headers)

```


#Clean data
```{r}

s18_pre_post <- s18_pre_post %>% 
  select(Final_ID, starts_with("k0"), starts_with("k5"), contains("bhvscl")) %>% 
  filter(!is.na(k0start), !is.na(k5start))

f18_pre <- f18_pre %>% 
  select(MENTEE_ID, starts_with("k0")) %>% 
  arrange(MENTEE_ID)

f18_post <- f18_post %>% 
  select(MENTEE_ID, starts_with("k1")) %>% 
  arrange(MENTEE_ID)

f_18_pre_post <- f18_pre %>% 
  left_join(f18_post, by = "MENTEE_ID") %>% 
  filter(str_length(MENTEE_ID) == 7)

f18_drop <- f18_drop %>% 
  mutate("drop" = `before/after program began?`,
          drop = str_to_lower(drop),
          drop_num = ifelse(drop != "before", 1,0)) %>% 
  select(MENTEE_ID, drop_num) %>% 
  arrange(MENTEE_ID)

f18_drop <- f18_drop %>% 
  full_join(f18_intake, by = "MENTEE_ID") %>% 
  select(MENTEE_ID, drop_num) %>% 
  filter(drop_num == 1 | is.na(drop_num)) %>% 
  mutate(drop_num = ifelse(is.na(drop_num), 0, drop_num))

s18_drop <- master%>% 
  filter(is.na(no_start)) %>% 
  select(MENTEE_ID = "Final_ID", drop_num = "date_dropped") %>% 
  mutate(drop_num = ifelse(!is.na(drop_num), 1, 0))

drop <- bind_rows(f18_drop, s18_drop)

  

```


#Objective 2.2
##Attendance & Mentor Pair
```{r}


per_drop <- drop %>% 
  summarize(perc_drop = mean(drop_num) * 100)

per_drop



```


100% of mentees were matched in 2018, and only `r paste0(round(per_drop$perc_drop,2), "%")` of the 226 youth dropped from the program.


##Substance use reduce
##Set-up
```{r}

s18_del <- s18_pre_post %>% 
  select(MENTEE_ID = "Final_ID", contains("dlq"))


f18_del <- f_18_pre_post %>% 
  select(MENTEE_ID, contains("dlq"))

namecon <- colnames(f18_del)
namecon <- str_replace(namecon, "k1", "k5")
colnames(f18_del) <- namecon

del <- bind_rows(s18_del, f18_del)



```

##2.2.1
```{r}
sub <- del %>% 
  select(MENTEE_ID, k0dlq_4:k0dlq_7, k5dlq_4:k5dlq_7) %>% 
  filter(k0dlq_4 >= 1 | k0dlq_5 >= 1 | k0dlq_6 >= 1 | k0dlq_7 >= 1) %>% 
  rowwise() %>% 
  mutate(k0sub = (k0dlq_4 + k0dlq_5 + k0dlq_6 + k0dlq_7),
         k5sub = (k5dlq_4 + k5dlq_5 + k5dlq_6 + k5dlq_7)) %>% 
  filter((!(is.na(k5sub))),
         (!(is.na(k0sub)))) %>% 
  mutate(sub_dec = ifelse(k5sub < k0sub, 1,0)) %>% 
  ungroup()
summarize(sub, Total = n(), substance_decrease = mean(sub_dec))
```


```{r}
nosub <- del %>% 
  select(MENTEE_ID, k0dlq_4:k0dlq_7, k5dlq_4:k5dlq_7) %>% 
  filter(k0dlq_4 == 0 & k0dlq_5 == 0 & k0dlq_6 == 0 & k0dlq_7 == 0) %>% 
  rowwise() %>% 
  mutate(k0sub = (k0dlq_4 + k0dlq_5 + k0dlq_6 + k0dlq_7),
         k5sub = (k5dlq_4 + k5dlq_5 + k5dlq_6 + k5dlq_7)) %>% 
  filter((!(is.na(k5sub))),
         (!(is.na(k0sub)))) %>% 
  mutate(no_use_post = ifelse(k5sub > 0, 0,1)) %>% 
  ungroup()

summarize(nosub, Total = n(), no_post_use = mean(no_use_post))
```

##Create Data set of those that have commited violent & property crimes
```{r}
crime <- del %>% 
  select(MENTEE_ID, k0dlq_1:k0dlq_2, k0dlq_3, k5dlq_1:k5dlq_10) %>%
  filter(k0dlq_1 > 0 | k0dlq_2 > 0 | k0dlq_3 > 0)
```


###Property crime pre-test vs post test (of youth who report pre-test)
```{r}
prop <- crime %>% 
  mutate(k0prdam = (k0dlq_1 + k0dlq_2),
         k5prdam = (k5dlq_1 + k5dlq_2)) %>% 
    filter((!(is.na(k0prdam))),
         (!(is.na(k5prdam)))) %>% 
  mutate(prop_decrease = ifelse(k5prdam < k0prdam, 1,0))
summarize(prop, Total = n(), prop_dam_decrease = mean(prop_decrease))
```


###Violence pretest vs post test (of youth who report pre-test)
```{r}
violent <- crime %>% 
  filter((!(is.na(k0dlq_3))),
        (!(is.na(k5dlq_3)))) %>% 
  mutate(violence_decrease = ifelse(k5dlq_3 < k0dlq_3, 1, 0))
summarize(violent, Total = n(), violence_decrease = mean(violence_decrease))
```

###Stealing
```{r}
steal <- del %>% 
  select(MENTEE_ID, k0dlq_9, k0dlq_10, k5dlq_9, k5dlq_10) %>% 
  mutate(k0steal = (k0dlq_9 + k0dlq_10),
         k5steal = (k5dlq_9 + k5dlq_10)) %>% 
  filter((!(is.na(k0steal))),
        (!(is.na(k5steal))),
        (k0steal != 0))%>% 
 mutate(steal_decrease = ifelse(k5steal < k0steal, 1,0))
  
summarize(steal, Total = n(), steal_decrease = mean(steal_decrease))
```


#Attendance
##Set-up
```{r}

s18_att <- s18_pre_post %>% 
  select(MENTEE_ID = "Final_ID", contains("bhvscl"))

namecon <- colnames(s18_att)
namecon <- str_replace(namecon, "k1", "k0")
colnames(s18_att) <- namecon
rm(namecon)

f18_att <- f_18_pre_post %>% 
  select(MENTEE_ID, contains("bhvscl"))

namecon <- colnames(f18_att)
namecon <- str_replace(namecon, "k1", "k5")
colnames(f18_att) <- namecon
rm(namecon)

att <- bind_rows(s18_att, f18_att)

att <- att %>% 
  select(MENTEE_ID, ends_with("_8"), ends_with("_9")) %>% 
  mutate(pre_att  = (k0bhvscl_8 + k0bhvscl_9),
         post_att = (k5bhvscl_8 + k5bhvscl_9)) %>% 
  filter(!is.na(pre_att),
         !is.na(post_att))
```

#preintervention attendendance problems
```{r}

att_prob <- att %>%
  filter(pre_att > 0) %>% 
  mutate(att_impr = ifelse(post_att < pre_att, 1,0))

summarize(att_prob, n = n(), att_improvement = mean(att_impr))

```

#preintervention attendendance problems
```{r}

att_good <- att %>%
  filter(pre_att == 0) %>% 
  mutate(att_impr = ifelse(post_att == pre_att, 1,0))

summarize(att_good, n = n(), att_same = mean(att_impr))

```
