---
title: "R Notebook for Network & belongingness Paper"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float:
      collapsed: yes
  html_document:
    df_print: paged
    toc: yes
    toc_float:
      collapsed: yes
---

#Introduction

#Clear Environment
```{r}
rm(list = ls(all.names = TRUE))
```

#Load Libraries
```{r, message = FALSE}
#install.packages("CTT")
#install.packages("GGally")
#install.packages("ggplot2")
#install.packages("lattice")
#install.packages("gridExtra")
#install.packages("igraph")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("igraph")
#install.packages("statnet")

library(CTT)
library(GGally)
library(ggplot2)
library(lattice)
library(gridExtra)
library(reshape)
library(igraph)
library(tidyverse)
```

#setwd & load data
```{r, message = FALSE, warning = FALSE}
setwd("T:/Research folders/CCWTG/Analyses/Data for Stats Dept/FINAL DATA")

#elmk <- read_csv("CC_edgelist.csv") 
#saveRDS(elmk,"cc_edgelist.rds")
elmk <- readRDS("cc_edgelist.rds")
youth_att <- read_csv("Mentee_Attributes.csv")
staff_att <- read_csv("Staff_Attributes_Final.csv")
```

#Format Edgelist
```{r}
elmk <- elmk %>% 
  filter(Receiver_Missing == 0,
         Sender_missing == 0, 
         Sender_Final_ID != Receiver_Final_ID) %>% 
  mutate(sn1 = ifelse((sn1 == 1 & sn2 == 0), NA, sn1), #marking NA for nominated, but weight = 0
         sn2 = ifelse(is.na(sn1), NA, sn2)) %>% 
  select(-Receiver_Missing, -Sender_missing)
```

#Format Attributes
```{r}

youth_att <- youth_att %>% 
  mutate(Final_ID = final_ID, 
         role1 = Role, 
         night1 = tolower(night),
         night2 =NA,
         role2 = NA,
         mentee = NA
         ) %>% 
  select(Final_ID, semester, night1, night2, mfcond, role1, role2, room, gender, mentee, impnotes, date_dropped, no_start)

staff_att <- staff_att %>% 
  mutate(date_dropped = NA,
         no_start = NA,
         Final_ID = FInal_ID) %>% 
  select(Final_ID, semester, night1, night2, mfcond, role1, role2, room, gender, mentee, impnotes, date_dropped, no_start)

staff_youth_att <- rbind(staff_att, youth_att)

staff_youth_att <- staff_youth_att %>% 
    #Easier to work with numbers
  mutate(role_num = ifelse(role1 == "mentee", 0, NA),
         role_num = ifelse(role1 == "mentor", 1, role_num),
         role_num = ifelse(role1 == "mentor coach", 2, role_num),
         role_num = ifelse(role1 == "lead mentor coach", 3, role_num),
         role_num = ifelse(role1 == "instructor", 4, role_num),
         role_num = ifelse(role1 == "Instructor", 4, role_num),
         
         role1 = ifelse(role1 == "Instructor", "instructor", role1),
         #Set role colors
         role_col = ifelse(role_num == 0, "orange", NA),
         role_col = ifelse(role_num == 1, "green", role_col),
         role_col = ifelse(role_num == 2, "dodgerblue", role_col),
         role_col = ifelse(role_num == 3, "red", role_col),
         role_col = ifelse(role_num == 4, "grey50", role_col)
         )
```


#Create General Graphs
##F15
```{r}
temp <- elmk %>% filter(semester == "F15")

mon <- temp %>% filter(night == "monday")
tue <- temp %>% filter(night == "tuesday")
wed <- temp %>% filter(night == "wednesday")
thu <- temp %>% filter(night == "thursday")

sem <- list(mon = mon, 
            tue = tue, 
            wed = wed, 
            thu = thu)

rm(mon);rm(tue);rm(wed);rm(thu)


```

**Summary**
```{r}


sem$mon <- group_by(sem$mon, survnum)
sem$tue <- group_by(sem$tue, survnum)
sem$wed <- group_by(sem$wed, survnum)
sem$thu <- group_by(sem$thu, survnum)

summarize(sem$mon, day = "mon", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$mon))*100)
summarize(sem$tue, day = "tue", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$tue))*100)
summarize(sem$wed, day = "wed", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$wed))*100)
summarize(sem$thu, day = "thu", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$thu))*100)

sem$mon <- ungroup(sem$mon)
sem$tue <- ungroup(sem$tue)
sem$wed <- ungroup(sem$wed)
sem$thu <- ungroup(sem$thu)
```

**Monday**
```{r}

temp_night <- temp %>% filter(night == "monday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create Monday List**
```{r}
monday <- list(edgelists = day, graphs = graphs)
rm(day);rm(graphs)
```


**Tuesday**
```{r}

temp_night <- temp %>% filter(night == "tuesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
tuesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Wednesday**
```{r}

temp_night <- temp %>% filter(night == "wednesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
wednesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Thursday**
```{r}

temp_night <- temp %>% filter(night == "thursday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```
**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```


**Create List**
```{r}
thursday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```

###Plot Graphs
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo = FALSE}

par(mfrow=c(5,4)) # To plot two plots side-by-side
#Week 1
plot(monday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g1),
     main = "Monday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g1),
     main = "Tuesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g1),
     main = "Wednesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g1),
     main = "Thursday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 3
plot(monday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g2),
     main = "Monday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g2),
     main = "Tuesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g2),
     main = "Wednesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g2),
     main = "Thursday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 6
plot(monday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g3),
     main = "Monday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g3),
     main = "Tuesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g3),
     main = "Wednesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g3),
     main = "Thursday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 9
plot(monday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g4),
     main = "Monday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g4),
     main = "Tuesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g4),
     main = "Wednesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g4),
     main = "Thursday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 11
plot(monday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g5),
     main = "Monday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


plot(tuesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g5),
     main = "Tuesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g5),
     main = "Wednesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g5),
     main = "Thursday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

```


**Create Semester List**
```{r}
F15 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
rm(temp)
```

##S16
```{r}
temp <- elmk %>% filter(semester == "S16")

mon <- temp %>% filter(night == "monday")
tue <- temp %>% filter(night == "tuesday")
wed <- temp %>% filter(night == "wednesday")
thu <- temp %>% filter(night == "thursday")

sem <- list(mon = mon, 
            tue = tue, 
            wed = wed, 
            thu = thu)

rm(mon);rm(tue);rm(wed);rm(thu)


```

**Summary**

```{r}


sem$mon <- group_by(sem$mon, survnum)
sem$tue <- group_by(sem$tue, survnum)
sem$wed <- group_by(sem$wed, survnum)
sem$thu <- group_by(sem$thu, survnum)

summarize(sem$mon, day = "mon", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$mon))*100)
summarize(sem$tue, day = "tue", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$tue))*100)
summarize(sem$wed, day = "wed", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$wed))*100)
summarize(sem$thu, day = "thu", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$thu))*100)

sem$mon <- ungroup(sem$mon)
sem$tue <- ungroup(sem$tue)
sem$wed <- ungroup(sem$wed)
sem$thu <- ungroup(sem$thu)
```

**Monday**
```{r}

temp_night <- temp %>% filter(night == "monday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```
**Create List**
```{r}
monday <- list(edgelists = day, graphs = graphs)
rm(day);rm(graphs)
```


**Tuesday**
```{r}

temp_night <- temp %>% filter(night == "tuesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
tuesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Wednesday**
```{r}

temp_night <- temp %>% filter(night == "wednesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
wednesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Thursday**
```{r}

temp_night <- temp %>% filter(night == "thursday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
thursday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


###Plot Graphs
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo = FALSE}

par(mfrow=c(5,4)) # To plot two plots side-by-side
#Week 1
plot(monday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g1),
     main = "Monday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g1),
     main = "Tuesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g1),
     main = "Wednesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g1),
     main = "Thursday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 3
plot(monday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g2),
     main = "Monday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g2),
     main = "Tuesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g2),
     main = "Wednesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g2),
     main = "Thursday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 6
plot(monday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g3),
     main = "Monday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g3),
     main = "Tuesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g3),
     main = "Wednesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g3),
     main = "Thursday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 9
plot(monday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g4),
     main = "Monday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g4),
     main = "Tuesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g4),
     main = "Wednesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g4),
     main = "Thursday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 11
plot(monday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g5),
     main = "Monday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


plot(tuesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g5),
     main = "Tuesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g5),
     main = "Wednesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g5),
     main = "Thursday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

```


**Create Semester List**
```{r}
S16 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
rm(temp)
```


##F16
```{r}
temp <- elmk %>% filter(semester == "F16")

mon <- temp %>% filter(night == "monday")
tue <- temp %>% filter(night == "tuesday")
wed <- temp %>% filter(night == "wednesday")
thu <- temp %>% filter(night == "thursday")

sem <- list(mon = mon, 
            tue = tue, 
            wed = wed, 
            thu = thu)

rm(mon);rm(tue);rm(wed);rm(thu)


```

**Summary**
```{r}


sem$mon <- group_by(sem$mon, survnum)
sem$tue <- group_by(sem$tue, survnum)
sem$wed <- group_by(sem$wed, survnum)
sem$thu <- group_by(sem$thu, survnum)

summarize(sem$mon, day = "mon", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$mon))*100)
summarize(sem$tue, day = "tue", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$tue))*100)
summarize(sem$wed, day = "wed", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$wed))*100)
summarize(sem$thu, day = "thu", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$thu))*100)

sem$mon <- ungroup(sem$mon)
sem$tue <- ungroup(sem$tue)
sem$wed <- ungroup(sem$wed)
sem$thu <- ungroup(sem$thu)
```

**Monday**
```{r}

temp_night <- temp %>% filter(night == "monday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
monday <- list(edgelists = day, graphs = graphs)
rm(day);rm(graphs)
```

**Tuesday**
```{r}

temp_night <- temp %>% filter(night == "tuesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
tuesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Wednesday**
```{r}

temp_night <- temp %>% filter(night == "wednesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
wednesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Thursday**
```{r}

temp_night <- temp %>% filter(night == "thursday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```
**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
thursday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```

###Plot Graphs
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo = FALSE}

par(mfrow=c(5,4)) # To plot two plots side-by-side
#Week 1
plot(monday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g1),
     main = "Monday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g1),
     main = "Tuesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g1),
     main = "Wednesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g1),
     main = "Thursday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 3
plot(monday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g2),
     main = "Monday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g2),
     main = "Tuesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g2),
     main = "Wednesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g2),
     main = "Thursday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 6
plot(monday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g3),
     main = "Monday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g3),
     main = "Tuesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g3),
     main = "Wednesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g3),
     main = "Thursday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 9
plot(monday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g4),
     main = "Monday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g4),
     main = "Tuesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g4),
     main = "Wednesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g4),
     main = "Thursday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 11
plot(monday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g5),
     main = "Monday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


plot(tuesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g5),
     main = "Tuesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g5),
     main = "Wednesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g5),
     main = "Thursday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

```



**Create Semester List**
```{r}
F16 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
rm(temp)
```


##S17
```{r}
temp <- elmk %>% filter(semester == "S17")

mon <- temp %>% filter(night == "monday")
tue <- temp %>% filter(night == "tuesday")
wed <- temp %>% filter(night == "wednesday")
thu <- temp %>% filter(night == "thursday")

sem <- list(mon = mon, 
            tue = tue, 
            wed = wed, 
            thu = thu)

rm(mon);rm(tue);rm(wed);rm(thu)


```

**Summary**

```{r}


sem$mon <- group_by(sem$mon, survnum)
sem$tue <- group_by(sem$tue, survnum)
sem$wed <- group_by(sem$wed, survnum)
sem$thu <- group_by(sem$thu, survnum)

summarize(sem$mon, day = "mon", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$mon))*100)
summarize(sem$tue, day = "tue", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$tue))*100)
summarize(sem$wed, day = "wed", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$wed))*100)
summarize(sem$thu, day = "thu", n = length(unique(Sender_Final_ID)), tie_count = sum(sn1, na.rm = TRUE), tie_prop = (tie_count/nrow(sem$thu))*100)

sem$mon <- ungroup(sem$mon)
sem$tue <- ungroup(sem$tue)
sem$wed <- ungroup(sem$wed)
sem$thu <- ungroup(sem$thu)
```

**Monday**
```{r}

temp_night <- temp %>% filter(night == "monday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
monday <- list(edgelists = day, graphs = graphs)
rm(day);rm(graphs)
```


**Tuesday**
```{r}

temp_night <- temp %>% filter(night == "tuesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```
**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
tuesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Wednesday**
```{r}

temp_night <- temp %>% filter(night == "wednesday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
wednesday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


**Thursday**
```{r}

temp_night <- temp %>% filter(night == "thursday")

#Surv_1
surv_1 <- temp_night %>% 
  filter(survnum == 1) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates1 <- surv_1 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_1 <- surv_1 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 2
surv_2 <- temp_night %>% 
  filter(survnum == 2) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates2 <- surv_2 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_2 <- surv_2 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 3
surv_3 <- temp_night %>% 
  filter(survnum == 3) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates3 <- surv_3 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_3 <- surv_3 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 4
surv_4 <- temp_night %>% 
  filter(survnum == 4) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates4 <- surv_4 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_4 <- surv_4 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

#Surv 5
surv_5 <- temp_night %>% 
  filter(survnum == 5) %>% 
  mutate(Receiver_Final_ID = ifelse(is.na(sn1), NA, Receiver_Final_ID)) #%>% 
#Getting isolates
isolates5 <- surv_5 %>% 
  mutate(sn1 = ifelse(is.na(sn1), 0, sn1)) %>% 
  group_by(Sender_Final_ID) %>% 
  summarize(isolate = sum(sn1)) %>% 
  filter(isolate < 1) %>% 
  select(Sender_Final_ID)
surv_5 <- surv_5 %>% 
   select(Sender_Final_ID, Receiver_Final_ID) %>% filter(!(is.na(Receiver_Final_ID)))

day <- list(sur1 = surv_1, 
            sur2 = surv_2, 
            sur3 = surv_3, 
            sur4 = surv_4,
            sur5 = surv_5,
            iso1 = isolates1,
            iso2 = isolates2,
            iso3 = isolates3,
            iso4 = isolates4,
            iso5 = isolates5)

rm(surv_1);rm(surv_2);rm(surv_3);rm(surv_4);rm(surv_5)
rm(isolates1);rm(isolates2);rm(isolates3);rm(isolates4);rm(isolates5)
rm(temp_night)

```

**General Graphs**
```{r, warning = FALSE}
sur1 <- as.matrix(day$sur1)
sur2 <- as.matrix(day$sur2)
sur3 <- as.matrix(day$sur3)
sur4 <- as.matrix(day$sur4)
sur5 <- as.matrix(day$sur5)


# Convert friends matrix to an igraph object
g1 <- graph.edgelist(sur1, directed = TRUE) + vertices(day$iso1$Sender_Final_ID) 
g2 <- graph.edgelist(sur2, directed = TRUE) + vertices(day$iso2$Sender_Final_ID) 
g3 <- graph.edgelist(sur3, directed = TRUE) + vertices(day$iso3$Sender_Final_ID) 
g4 <- graph.edgelist(sur4, directed = TRUE) + vertices(day$iso4$Sender_Final_ID) 
g5 <- graph.edgelist(sur5, directed = TRUE) + vertices(day$iso5$Sender_Final_ID) 

#Add staff Attribute  & colors

V(g1)$role  <- staff_youth_att$role1[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g1)$color <- staff_youth_att$role_col[match(V(g1)$name, staff_youth_att$Final_ID)] 
V(g2)$role  <- staff_youth_att$role1[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g2)$color <- staff_youth_att$role_col[match(V(g2)$name, staff_youth_att$Final_ID)] 
V(g3)$role  <- staff_youth_att$role1[match(V(g3)$name, staff_youth_att$Final_ID)] 
V(g3)$color <- staff_youth_att$role_col[match(V(g3)$name, staff_youth_att$Final_ID)]
V(g4)$role  <- staff_youth_att$role1[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g4)$color <- staff_youth_att$role_col[match(V(g4)$name, staff_youth_att$Final_ID)] 
V(g5)$role  <- staff_youth_att$role1[match(V(g5)$name, staff_youth_att$Final_ID)] 
V(g5)$color <- staff_youth_att$role_col[match(V(g5)$name, staff_youth_att$Final_ID)] 


graphs <- list(g1 = g1,g2 = g2, g3 = g3,g4 = g4, g5 = g5)

role <-  c("mentee", "mentor", "mentor coach", "lead mentor coach", "instructor") 
color <- c("orange","green","dodgerblue", "red", "grey50")


rm(g1); rm(g2); rm(g3); rm(g4); rm(g5)
rm(sur1);rm(sur2);rm(sur3);rm(sur4);rm(sur5)
```

**Create List**
```{r}
thursday <- list(edgelists = day, graphs = graphs)
rm(day); rm(graphs)
```


###Plot Graphs
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo = FALSE}

par(mfrow=c(5,4)) # To plot two plots side-by-side
#Week 1
plot(monday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g1),
     main = "Monday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g1),
     main = "Tuesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g1),
     main = "Wednesday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g1,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g1),
     main = "Thursday - Week 1")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 3
plot(monday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g2),
     main = "Monday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g2),
     main = "Tuesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g2),
     main = "Wednesday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g2,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g2),
     main = "Thursday - Week 3")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 6
plot(monday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g3),
     main = "Monday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g3),
     main = "Tuesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g3),
     main = "Wednesday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g3,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g3),
     main = "Thursday - Week 6")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


#Week 9
plot(monday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g4),
     main = "Monday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(tuesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g4),
     main = "Tuesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g4),
     main = "Wednesday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g4,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g4),
     main = "Thursday - Week 9")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

#Week 11
plot(monday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(monday$graphs$g5),
     main = "Monday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))


plot(tuesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(tuesday$graphs$g5),
     main = "Tuesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(wednesday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(wednesday$graphs$g5),
     main = "Wednesday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

plot(thursday$graphs$g5,
     vertex.label = NA, 
     vertex.size = 10,
     edge.color = 'black',
     edge.arrow.size = 0.05,
     layout = layout_nicely(thursday$graphs$g5),
     main = "Thursday - Week 11")
legend("bottomright", legend=role  , col = color , bty = "o", pch=20 , pt.cex = 1, cex = 1, text.col= color , horiz = FALSE, inset = c(-0.06, 0))

```


**Create Semester List**
```{r}
S17 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
rm(temp)
```


#Combine Semesters to list
```{r}
ALL <- list(F15 = F15, S16 = S16, F16 = F16, S17 = S17)
rm(F15);rm(S16);rm(F16);rm(S17)
```

#Examine Cliques
##F15
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo=FALSE}

#Monday
g1 <- ALL$F15$monday$graphs$g1
g2 <- ALL$F15$monday$graphs$g2
g3 <- ALL$F15$monday$graphs$g3
g4 <- ALL$F15$monday$graphs$g4
g5 <- ALL$F15$monday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

monday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

#Tuesday
g1 <- ALL$F15$tuesday$graphs$g1
g2 <- ALL$F15$tuesday$graphs$g2
g3 <- ALL$F15$tuesday$graphs$g3
g4 <- ALL$F15$tuesday$graphs$g4
g5 <- ALL$F15$tuesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

tuesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Wednesday
g1 <- ALL$F15$wednesday$graphs$g1
g2 <- ALL$F15$wednesday$graphs$g2
g3 <- ALL$F15$wednesday$graphs$g3
g4 <- ALL$F15$wednesday$graphs$g4
g5 <- ALL$F15$wednesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

wednesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Thursday
g1 <- ALL$F15$thursday$graphs$g1
g2 <- ALL$F15$thursday$graphs$g2
g3 <- ALL$F15$thursday$graphs$g3
g4 <- ALL$F15$thursday$graphs$g4
g5 <- ALL$F15$thursday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

thursday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

par(mfrow=c(5,4))
plot(monday$surv1, main =    "week 1 - Monday")
plot(tuesday$surv1, main =   "week 1 - Tuesday")
plot(wednesday$surv1, main = "week 1 - Wednesday")
plot(thursday$surv1, main =  "week 1 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv2, main =    "week 3 - Monday")
plot(tuesday$surv2, main =   "week 3 - Tuesday")
plot(wednesday$surv2, main = "week 3 - Wednesday")
plot(thursday$surv2, main =  "week 3 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv3, main =    "week 6 - Monday")
plot(tuesday$surv3, main =   "week 6 - Tuesday")
plot(wednesday$surv3, main = "week 6 - Wednesday")
plot(thursday$surv3, main =  "week 6 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv4, main =    "week 9 - Monday")
plot(tuesday$surv4, main =   "week 9 - Tuesday")
plot(wednesday$surv4, main = "week 9 - Wednesday")
plot(thursday$surv4, main =  "week 9 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv5, main =    "week 11 - Monday")
plot(tuesday$surv5, main =   "week 11 - Tuesday")
plot(wednesday$surv5, main = "week 11 - Wednesday")
plot(thursday$surv5, main =  "week 11 -Thursday")

F15 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
```

##S16
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo=FALSE}

#Monday
g1 <- ALL$S16$monday$graphs$g1
g2 <- ALL$S16$monday$graphs$g2
g3 <- ALL$S16$monday$graphs$g3
g4 <- ALL$S16$monday$graphs$g4
g5 <- ALL$S16$monday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

monday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

#Tuesday
g1 <- ALL$S16$tuesday$graphs$g1
g2 <- ALL$S16$tuesday$graphs$g2
g3 <- ALL$S16$tuesday$graphs$g3
g4 <- ALL$S16$tuesday$graphs$g4
g5 <- ALL$S16$tuesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

tuesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Wednesday
g1 <- ALL$S16$wednesday$graphs$g1
g2 <- ALL$S16$wednesday$graphs$g2
g3 <- ALL$S16$wednesday$graphs$g3
g4 <- ALL$S16$wednesday$graphs$g4
g5 <- ALL$S16$wednesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

wednesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Thursday
g1 <- ALL$S16$thursday$graphs$g1
g2 <- ALL$S16$thursday$graphs$g2
g3 <- ALL$S16$thursday$graphs$g3
g4 <- ALL$S16$thursday$graphs$g4
g5 <- ALL$S16$thursday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

thursday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

par(mfrow=c(5,4))
plot(monday$surv1, main =    "week 1 - Monday")
plot(tuesday$surv1, main =   "week 1 - Tuesday")
plot(wednesday$surv1, main = "week 1 - Wednesday")
plot(thursday$surv1, main =  "week 1 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv2, main =    "week 3 - Monday")
plot(tuesday$surv2, main =   "week 3 - Tuesday")
plot(wednesday$surv2, main = "week 3 - Wednesday")
plot(thursday$surv2, main =  "week 3 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv3, main =    "week 6 - Monday")
plot(tuesday$surv3, main =   "week 6 - Tuesday")
plot(wednesday$surv3, main = "week 6 - Wednesday")
plot(thursday$surv3, main =  "week 6 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv4, main =    "week 9 - Monday")
plot(tuesday$surv4, main =   "week 9 - Tuesday")
plot(wednesday$surv4, main = "week 9 - Wednesday")
plot(thursday$surv4, main =  "week 9 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv5, main =    "week 11 - Monday")
plot(tuesday$surv5, main =   "week 11 - Tuesday")
plot(wednesday$surv5, main = "week 11 - Wednesday")
plot(thursday$surv5, main =  "week 11 -Thursday")


S16<- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
```



##F16
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo=FALSE}

#Monday
g1 <- ALL$F16$monday$graphs$g1
g2 <- ALL$F16$monday$graphs$g2
g3 <- ALL$F16$monday$graphs$g3
g4 <- ALL$F16$monday$graphs$g4
g5 <- ALL$F16$monday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

monday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

#Tuesday
g1 <- ALL$F16$tuesday$graphs$g1
g2 <- ALL$F16$tuesday$graphs$g2
g3 <- ALL$F16$tuesday$graphs$g3
g4 <- ALL$F16$tuesday$graphs$g4
g5 <- ALL$F16$tuesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

tuesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Wednesday
g1 <- ALL$F16$wednesday$graphs$g1
g2 <- ALL$F16$wednesday$graphs$g2
g3 <- ALL$F16$wednesday$graphs$g3
g4 <- ALL$F16$wednesday$graphs$g4
g5 <- ALL$F16$wednesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

wednesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Thursday
g1 <- ALL$F16$thursday$graphs$g1
g2 <- ALL$F16$thursday$graphs$g2
g3 <- ALL$F16$thursday$graphs$g3
g4 <- ALL$F16$thursday$graphs$g4
g5 <- ALL$F16$thursday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

thursday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

par(mfrow=c(5,4))
plot(monday$surv1, main =    "week 1 - Monday")
plot(tuesday$surv1, main =   "week 1 - Tuesday")
plot(wednesday$surv1, main = "week 1 - Wednesday")
plot(thursday$surv1, main =  "week 1 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv2, main =    "week 3 - Monday")
plot(tuesday$surv2, main =   "week 3 - Tuesday")
plot(wednesday$surv2, main = "week 3 - Wednesday")
plot(thursday$surv2, main =  "week 3 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv3, main =    "week 6 - Monday")
plot(tuesday$surv3, main =   "week 6 - Tuesday")
plot(wednesday$surv3, main = "week 6 - Wednesday")
plot(thursday$surv3, main =  "week 6 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv4, main =    "week 9 - Monday")
plot(tuesday$surv4, main =   "week 9 - Tuesday")
plot(wednesday$surv4, main = "week 9 - Wednesday")
plot(thursday$surv4, main =  "week 9 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv5, main =    "week 11 - Monday")
plot(tuesday$surv5, main =   "week 11 - Tuesday")
plot(wednesday$surv5, main = "week 11 - Wednesday")
plot(thursday$surv5, main =  "week 11 -Thursday")

F16 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
```




##S17
```{r, warning = FALSE, fig.width = 20, fig.height=20, echo=FALSE}

#Monday
g1 <- ALL$S17$monday$graphs$g1
g2 <- ALL$S17$monday$graphs$g2
g3 <- ALL$S17$monday$graphs$g3
g4 <- ALL$S17$monday$graphs$g4
g5 <- ALL$S17$monday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

monday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

#Tuesday
g1 <- ALL$S17$tuesday$graphs$g1
g2 <- ALL$S17$tuesday$graphs$g2
g3 <- ALL$S17$tuesday$graphs$g3
g4 <- ALL$S17$tuesday$graphs$g4
g5 <- ALL$S17$tuesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

tuesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Wednesday
g1 <- ALL$S17$wednesday$graphs$g1
g2 <- ALL$S17$wednesday$graphs$g2
g3 <- ALL$S17$wednesday$graphs$g3
g4 <- ALL$S17$wednesday$graphs$g4
g5 <- ALL$S17$wednesday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

wednesday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)


#Thursday
g1 <- ALL$S17$thursday$graphs$g1
g2 <- ALL$S17$thursday$graphs$g2
g3 <- ALL$S17$thursday$graphs$g3
g4 <- ALL$S17$thursday$graphs$g4
g5 <- ALL$S17$thursday$graphs$g5


lc1 <- largest_cliques(g1) 
gs1 <- as.undirected(induced.subgraph(g1, lc1[[1]]))

lc1 <- largest_cliques(g2) 
gs2 <- as.undirected(induced.subgraph(g2, lc1[[1]]))

lc1 <- largest_cliques(g3) 
gs3 <- as.undirected(induced.subgraph(g3, lc1[[1]]))

lc1 <- largest_cliques(g4) 
gs4 <- as.undirected(induced.subgraph(g4, lc1[[1]]))

lc1 <- largest_cliques(g5) 
gs5 <- as.undirected(induced.subgraph(g5, lc1[[1]]))

thursday <- list(surv1 = gs1, surv2 = gs2, surv3 = gs3, surv4 = gs4, surv5 = gs5)

rm(g1);rm(g2);rm(g3);rm(g4);rm(g5);
rm(gs1);rm(gs2);rm(gs3);rm(gs4);rm(gs5)

par(mfrow=c(5,4))
plot(monday$surv1, main =    "week 1 - Monday")
plot(tuesday$surv1, main =   "week 1 - Tuesday")
plot(wednesday$surv1, main = "week 1 - Wednesday")
plot(thursday$surv1, main =  "week 1 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv2, main =    "week 3 - Monday")
plot(tuesday$surv2, main =   "week 3 - Tuesday")
plot(wednesday$surv2, main = "week 3 - Wednesday")
plot(thursday$surv2, main =  "week 3 -Thursday")

#par(mfrow=c(4,1))
plot(monday$surv3, main =    "week 6 - Monday")
plot(tuesday$surv3, main =   "week 6 - Tuesday")
plot(wednesday$surv3, main = "week 6 - Wednesday")
plot(thursday$surv3, main =  "week 6 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv4, main =    "week 9 - Monday")
plot(tuesday$surv4, main =   "week 9 - Tuesday")
plot(wednesday$surv4, main = "week 9 - Wednesday")
plot(thursday$surv4, main =  "week 9 -Thursday")


#par(mfrow=c(4,1))
plot(monday$surv5, main =    "week 11 - Monday")
plot(tuesday$surv5, main =   "week 11 - Tuesday")
plot(wednesday$surv5, main = "week 11 - Wednesday")
plot(thursday$surv5, main =  "week 11 -Thursday")

S17 <- list(monday = monday, tuesday = tuesday, wednesday = wednesday, thursday = thursday)
rm(monday);rm(tuesday);rm(wednesday);rm(thursday)
```
##Combine Cliques
```{r}
cliques <- list(F15 = F15, S16 = S16, F16 = F16, S17 = S17)
rm(F15);rm(S16);rm(F16);rm(S17)
```

