---
title: 'R Notebook: Predictors of Dropout'
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---
#clear environment
```{r}
rm(list = ls(all.names = TRUE))
```


#Load library
```{r, message = FALSE, warning = FALSE}
#install.packages("lavaan")
#install.packages("xtable")
#install.packages("kableExtra")
#install.packages("semPlot")

library(tidyverse)
library(lavaan)
library(GGally)
library(xtable)
library("kableExtra")
library(knitr)
library(semPlot)
```

#Load Data
```{r, message = FALSE, warning = FALSE}

setwd("T:/Research folders/CCWTG/Analyses/Papers/Dropout/lavaan")

att  <-   read_csv("R_pois.csv")
drop <-   read_csv("R_log.csv")
```

#Subset items
```{r}
sem_items <- drop %>% 
  select(risk_1:risk_32)

items <- c("risk_1","risk_2","risk_3","risk_4","risk_5","risk_6","risk_7","risk_8","risk_9","risk_10","risk_11","risk_12","risk_13","risk_14","risk_15","risk_16","risk_17","risk_18","risk_19","risk_20","risk_21","risk_22","risk_23","risk_24","risk_25","risk_26","risk_27","risk_28","risk_29","risk_30","risk_31", "risk_32")
```

#Frequency table
```{r}
#Count responses: plyr::count
count_all <- map(sem_items, plyr::count)

#COnvert to datframe
count_all <-  as.data.frame(count_all)

#Get necessary info
count_all <- count_all %>% 
  mutate(selection = ifelse(risk_1.x == 1, "yes", NA),
         selection = ifelse(risk_1.x == 0, "no", selection)) %>% 
  select(selection, ends_with(".freq"))

count_all 
```


#Item corrlations
```{r rows.print=32}

cor <- round(cor(sem_items, use = "pairwise.complete.obs") ,2)

upper<-cor
upper[upper.tri(cor)]<-""
upper<-as.data.frame(upper)


kable(upper, "html", full_width = T)


#kable(upper, "html") %>%
#  kable_styling(full_width = T, position = "left") # <- nicer chart but only works whenknit to html. 

```


#Confirmatory Factor Analyses
##Models
```{r}
eco_risk <- "eco_risk  =~ risk_1 + risk_2 + risk_3 + risk_4 + risk_5 + risk_6 + risk_7"
fam_str  <- "fam_str   =~ risk_8 + risk_9 + risk_10 + risk_11 + risk_12 + risk_13 + risk_14 + risk_15 + risk_16 + risk_17 + risk_ 18"
peer_dif <- "peer_dif  =~ risk_19 + risk_20"

aca_cha  <- "aca_cha   =~ risk_21 + risk_22 + risk_23"    
prob_be  <- "prob_be   =~ risk_25 + risk_26 + risk_27 + risk_28  + risk_30  #+ risk_29"
men_he   <- "men_he    =~ risk_31 + risk_ 32"                            
```

##Economic Risk
```{r}
cfa <- cfa(eco_risk, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Family structure
```{r}
cfa <- cfa(fam_str, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Peer difficulties
```{r}
cfa <- cfa(peer_dif, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```


##Academic Challenges
```{r}
cfa <- cfa(aca_cha, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Problem Behavior
```{r}
cfa <- cfa(prob_be, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Mental Health Challenges
```{r}
cfa <- cfa(men_he, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

#SEM
##Models
Current problems with model convergence when idnetifying the overall environmental & individual risk factors scale. 
I will also take all items loaded onto the environmental & individual risk factors scale. This will be model 2.
```{r}

model1 <- "
       #Environmental risk factors
          eco_risk  =~ risk_1 + risk_2 + risk_3 + risk_4 + risk_5 + risk_6 + risk_7
          fam_str   =~ risk_8 + risk_9 + risk_10 + risk_11 + risk_12 + risk_13 + risk_14 + risk_15 + risk_16 + risk_17 + risk_ 18
          peer_dif  =~ risk_19 + risk_20
          
        #Individual Risk factors
          aca_cha   =~ risk_21 + risk_22 + risk_23                        #+risk_24
          prob_be   =~ risk_25 + risk_26 + risk_27 + risk_28  + risk_30   #+ risk_29
          men_he    =~ risk_31 + risk_ 32

        #env_risk =~ eco_risk + fam_str + peer_dif    
        #ind_risk =~ aca_cha + prob_be + men_he

        #risk =~ env_risk + ind_risk
"

model2 <- "
       #Environmental risk factors
          env_risk =~ risk_1 + risk_2 + risk_3 + risk_4 + risk_5 + risk_6 + risk_7 +
          risk_8 + risk_9 + risk_10 + risk_11 + risk_12 + risk_13 + risk_14 + risk_15 + risk_16 + risk_17 + risk_ 18 +
          risk_19 + risk_20
  
          
        #Individual Risk factors
         ind_risk   =~ risk_21 + risk_22 + risk_23 +                        #+risk_24
          risk_25 + risk_26 + risk_27 + risk_28  + risk_30 +   #+ risk_29
          risk_31 + risk_ 32

       # risk =~ env_risk + ind_risk
"
```

###Fit Model 1
```{r}
fit <-sem(model1, sem_items)
summary(fit, fit.measures =TRUE)

```


###Fit model 2
```{r}
fit2 <-sem(model2, sem_items)
summary(fit2, fit.measures =TRUE)
```

##Diagrams
##Model 1
```{r, fig.width= 20, fig.height= 20}

semPaths(fit, "std", title = FALSE, curvePivot = TRUE)
```
##Model 2
```{r, fig.width= 20, fig.height= 20}
semPaths(fit2, "std", title = FALSE, curvePivot = TRUE)
```