---
title: 'R Notebook: Predictors of Dropout'
output:
  html_notebook:
    toc: yes
    toc_float: yes
    self_contained: no
  pdf_document:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    self_contained: no
    theme: yeti
---
#clear environment
```{r}
rm(list = ls(all.names = TRUE))
```


#Load library
```{r, message = FALSE, warning = FALSE}
#install.packages("lavaan")
#install.packages("xtable")
#install.packages("kableExtra")
#install.packages("semPlot")
#install.packages("minqa")


library(tidyverse)
library(lavaan)
library(GGally)
library(xtable)
library("kableExtra")
library(knitr)
#library(semPlot)
library(knitr)
library(gridExtra)
library(reshape)
library(pander)
```

#Set Kim's Reliability Function
```{r, warning=FALSE, message=FALSE}

my_reliability <- function (items, itemal = TRUE, NA.Delete = TRUE) 
{
    if (!all(apply(items, c(1, 2), is.numeric))) {
        items <- apply(items, c(1, 2), as.numeric)
        warning("Data is not numeric. Data has been coerced to be numeric.")
    }
    if (NA.Delete == FALSE) {
        items[is.na(items)] <- 0
        warning("Missing values or NA values are converted to zeros.")
    }
    items <- na.omit(items)
    s <- apply(items, 2, var)
    N <- ncol(items)
    X <- rowSums(items)
    alpha <- (N/(N - 1)) * (1 - sum(s)/var(X))
    if (itemal) {
        alphad <- array(dim = N)
        pbis <- array(dim = N)
        for (i in 1:N) {
            Xd <- rowSums(items[, -i])
            Mean <- sapply(items, mean)
            SD <- sapply(items, sd)
            Min <- sapply(items, min)
            Max <- sapply(items, max)
            Nobs <- sapply(items, length)
            alphad[i] <- ((N - 1)/(N - 2)) * (1 - sum(s[-i])/var(Xd))
            pbis[i] <- cor(items[, i], Xd)
            out <- list(nItem = N, nPerson = nrow(items), alpha = alpha, 
                scaleMean = mean(X), scaleSD = sd(X), Alpha.If.Deleted = alphad, 
                R.With.Total = pbis, Mean = Mean, SD = SD, Min = Min, Max = Max, Nobs=Nobs)
        }
    }
    else out <- list(nItem = N, nPerson = nrow(items), alpha = alpha, 
        scaleMean = mean(X), scaleSD = sd(X))
    class(out) <- "my_reliability"
    out
}

print <- function(x, ...) {
    if (is.numeric(x)) base::print(round(x, digits=3), ...) 
    else base::print(x, ...)
}

```


#Load Data
```{r, message = FALSE, warning = FALSE}

setwd("T:/Research folders/CCWTG/Analyses/Papers/Dropout/lavaan")

att  <-   read_csv("R_pois.csv")
drop <-   read_csv("R_log.csv")
```

#Subset items
```{r}
sem_items <- drop %>% 
  select(risk_1:risk_32)

items <- c("risk_1","risk_2","risk_3","risk_4","risk_5","risk_6","risk_7","risk_8","risk_9","risk_10","risk_11","risk_12","risk_13","risk_14","risk_15","risk_16","risk_17","risk_18","risk_19","risk_20","risk_21","risk_22","risk_23","risk_24","risk_25","risk_26","risk_27","risk_28","risk_29","risk_30","risk_31", "risk_32")
```

#Frequency table
```{r}
#Count responses: plyr::count
count_all <- map(sem_items, plyr::count)

#COnvert to datframe
count_all <-  as.data.frame(count_all)

#Get necessary info
count_all <- count_all %>% 
  mutate(selection = ifelse(risk_1.x == 1, "yes", NA),
         selection = ifelse(risk_1.x == 0, "no", selection)) %>% 
  select(selection, ends_with(".freq"))

count_all 
```


#Item corrlations
```{r rows.print=32}

cor <- round(cor(sem_items, use = "pairwise.complete.obs") ,2)

upper<-cor
upper[upper.tri(cor)]<-""
upper<-as.data.frame(upper)


kable(upper, "html", full_width = T)


#kable(upper, "html") %>%
#  kable_styling(full_width = T, position = "left") # <- nicer chart but only works whenknit to html. 

```


#Confirmatory Factor Analyses
##Models
```{r}
eco_risk <- "eco_risk  =~ risk_1 + risk_2 + risk_3 + risk_4 + risk_5 + risk_6 + risk_7"
fam_str  <- "fam_str   =~ risk_8 + risk_9 + risk_10 + risk_11 + risk_12 + risk_13 + risk_14 + risk_15 + risk_16 + risk_17 + risk_18"
peer_dif <- "peer_dif  =~ risk_19 + risk_20"

aca_cha  <- "aca_cha   =~ risk_21 + risk_22 + risk_23"    
prob_be  <- "prob_be   =~ risk_25 + risk_26 + risk_27 + risk_28  + risk_30  #+ risk_29"
men_he   <- "men_he    =~ risk_31 + risk_32"                            
```

##Economic Risk

**Item Analysis**
```{r, message=FALSE, warning=FALSE}


items <- sem_items %>% 
	select(risk_1 , risk_2 , risk_3 , risk_4 , risk_5 , risk_6 , risk_7)

variables <- c("risk_1","risk_2","risk_3","risk_4","risk_5","risk_6","risk_7")
  

ca <- my_reliability(items, itemal=TRUE, NA.Delete=TRUE)

pipealpha <- paste(formatC(round(ca$alpha, digits=2), 2, format = "f"))


temp <- cbind.data.frame(variables, ca$Nobs, ca$Mean, ca$SD, ca$Min, ca$Max, ca$R.With.Total, ca$Alpha.If.Deleted)
colnames(temp) <- c("Item", "N", "Average", "Standard Deviation", "Minimum", "Maximum", "Correlation with total", "Cronbach's Alpha if item is deleted")
rownames(temp) <- NULL


```

*Cronbach's Alpha:* `r pipealpha`
```{r   col.print=32, message=FALSE, warning=FALSE}
set.alignment('center', row.names = 'center')
pander(temp)

rm(ca)
rm(temp)
rm(pipealpha)
```


```{r}
cfa <- cfa(eco_risk, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Family structure

**Item Analysis**
```{r, message=FALSE, warning=FALSE}


items <- sem_items %>% 
	select(risk_8 , risk_9 , risk_10 , risk_11 , risk_12 , risk_13 , risk_14 , risk_15 , risk_16 , risk_17 , risk_18)

variables <- c("risk_8","risk_9","risk_10","risk_11","risk_12","risk_13","risk_14","risk_15","risk_16","risk_17","risk_18")
  

ca <- my_reliability(items, itemal=TRUE, NA.Delete=TRUE)

pipealpha <- paste(formatC(round(ca$alpha, digits=2), 2, format = "f"))


temp <- cbind.data.frame(variables, ca$Nobs, ca$Mean, ca$SD, ca$Min, ca$Max, ca$R.With.Total, ca$Alpha.If.Deleted)
colnames(temp) <- c("Item", "N", "Average", "Standard Deviation", "Minimum", "Maximum", "Correlation with total", "Cronbach's Alpha if item is deleted")
rownames(temp) <- NULL


```

*Cronbach's Alpha:* `r pipealpha`
```{r, echo = FALSE}
set.alignment('center', row.names = 'center')
pander(temp)

rm(ca)
rm(temp)
rm(pipealpha)
```
```{r}
cfa <- cfa(fam_str, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Peer difficulties

**Item Analysis**
```{r, message=FALSE, warning=FALSE}


items <- sem_items %>% 
	select(risk_19 , risk_20)

variables <- c("risk_19","risk_20")
  

ca <- my_reliability(items, itemal=TRUE, NA.Delete=TRUE)

pipealpha <- paste(formatC(round(ca$alpha, digits=2), 2, format = "f"))


temp <- cbind.data.frame(variables, ca$Nobs, ca$Mean, ca$SD, ca$Min, ca$Max, ca$R.With.Total)
colnames(temp) <- c("Item", "N", "Average", "Standard Deviation", "Minimum", "Maximum", "Correlation with total")
rownames(temp) <- NULL


```

*Cronbach's Alpha* NA (2-items scale)
```{r, echo = FALSE}
set.alignment('center', row.names = 'center')
pander(temp)

rm(ca)
rm(temp)
rm(pipealpha)
```

```{r}
cfa <- cfa(peer_dif, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```


##Academic Challenges

**Item Analysis**
```{r, message=FALSE, warning=FALSE}


items <- sem_items %>% 
	select(risk_21 , risk_22 , risk_23, risk_24)

variables <- c("risk_21","risk_22","risk_23","risk_24")
  

ca <- my_reliability(items, itemal=TRUE, NA.Delete=TRUE)

pipealpha <- paste(formatC(round(ca$alpha, digits=2), 2, format = "f"))


temp <- cbind.data.frame(variables, ca$Nobs, ca$Mean, ca$SD, ca$Min, ca$Max, ca$R.With.Total, ca$Alpha.If.Deleted)
colnames(temp) <- c("Item", "N", "Average", "Standard Deviation", "Minimum", "Maximum", "Correlation with total", "Cronbach's Alpha if item is deleted")
rownames(temp) <- NULL


```

*Cronbach's Alpha:* `r pipealpha`
```{r, echo = FALSE}
set.alignment('center', row.names = 'center')
pander(temp)

rm(ca)
rm(temp)
rm(pipealpha)
```
```{r}
cfa <- cfa(aca_cha, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Problem Behavior

**Item Analysis**
```{r, message=FALSE, warning=FALSE}


items <- sem_items %>% 
	select(risk_25:risk_30)

variables <- c("risk_25","risk_26","risk_27","risk_28", "risk_29", "risk_30")
  

ca <- my_reliability(items, itemal=TRUE, NA.Delete=TRUE)

pipealpha <- paste(formatC(round(ca$alpha, digits=2), 2, format = "f"))


temp <- cbind.data.frame(variables, ca$Nobs, ca$Mean, ca$SD, ca$Min, ca$Max, ca$R.With.Total, ca$Alpha.If.Deleted)
colnames(temp) <- c("Item", "N", "Average", "Standard Deviation", "Minimum", "Maximum", "Correlation with total", "Cronbach's Alpha if item is deleted")
rownames(temp) <- NULL


```

*Cronbach's Alpha:* `r pipealpha`
```{r, echo = FALSE}
set.alignment('center', row.names = 'center')
pander(temp)

rm(ca)
rm(temp)
rm(pipealpha)
```
```{r}
cfa <- cfa(prob_be, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

##Mental Health Challenges

**Item Analysis**
```{r, message=FALSE, warning=FALSE}


items <- sem_items %>% 
	select( risk_31, risk_32)

variables <- c("risk_31","risk_32")
  

ca <- my_reliability(items, itemal=TRUE, NA.Delete=TRUE)

pipealpha <- paste(formatC(round(ca$alpha, digits=2), 2, format = "f"))


temp <- cbind.data.frame(variables, ca$Nobs, ca$Mean, ca$SD, ca$Min, ca$Max, ca$R.With.Total)
colnames(temp) <- c("Item", "N", "Average", "Standard Deviation", "Minimum", "Maximum", "Correlation with total")
rownames(temp) <- NULL


```

*Cronbach's Alpha* NA (2-items scale)
```{r, echo = FALSE}
set.alignment('center', row.names = 'center')
pander(temp)

rm(ca)
rm(temp)
rm(pipealpha)
```

```{r}
cfa <- cfa(men_he, data = sem_items)
summary(cfa, fit.measures = TRUE)
rm(cfa)
```

#SEM
##Models
Current problems with model convergence when idnetifying the overall environmental & individual risk factors scale. 
I will also take all items loaded onto the environmental & individual risk factors scale. This will be model 2.
```{r}

model1 <- "
       #Environmental risk factors
          eco_risk  =~ risk_1 + risk_2 + risk_3 + risk_4 + risk_5 + risk_6 + risk_7
          fam_str   =~ risk_8 + risk_9 + risk_10 + risk_11 + risk_12 + risk_13 + risk_14 + risk_15 + risk_16 + risk_17 + risk_18
          peer_dif  =~ risk_19 + risk_20
          
        #Individual Risk factors
          aca_cha   =~ risk_21 + risk_22 + risk_23                        #+risk_24
          prob_be   =~ risk_25 + risk_26 + risk_27 + risk_28  + risk_30   #+ risk_29
          men_he    =~ risk_31 + risk_32

        #env_risk =~ eco_risk + fam_str + peer_dif    
        #ind_risk =~ aca_cha + prob_be + men_he

        #risk =~ env_risk + ind_risk
"

model2 <- "
       #Environmental risk factors
          env_risk =~ risk_1 + risk_2 + risk_3 + risk_4 + risk_5 + risk_6 + risk_7 +
          risk_8 + risk_9 + risk_10 + risk_11 + risk_12 + risk_13 + risk_14 + risk_15 + risk_16 + risk_17 + risk_18 +
          risk_19 + risk_20
  
          
        #Individual Risk factors
         ind_risk   =~ risk_21 + risk_22 + risk_23 +                        #+risk_24
          risk_25 + risk_26 + risk_27 + risk_28  + risk_30 +   #+ risk_29
          risk_31 + risk_32

       # risk =~ env_risk + ind_risk
"
```

###Fit Model 1
```{r}
fit <-sem(model1, sem_items)
summary(fit, fit.measures =TRUE)

```


###Fit model 2
```{r}
fit2 <-sem(model2, sem_items)
summary(fit2, fit.measures =TRUE)
```

##Diagrams
##Model 1
```{r, fig.width= 20, fig.height= 20}

#semPaths(fit, "std", title = FALSE, curvePivot = TRUE)
```
##Model 2
```{r, fig.width= 20, fig.height= 20}
#semPaths(fit2, "std", title = FALSE, curvePivot = TRUE)
```